Privacy Analysis of a Mobile Sensor Application

### 2015-01-19 paper.tex
minor changes

In section \ref{subsec:world-analysis} and \ref{subsec:pot-analysis} we apply the first two steps of the Reference Model for IT Security Analysis as described in \cite{Grimm:ItSecRefModel}.  It supersedes earlier efforts by
e.g. \cite{Avizienis}.  The reference model consists of a \emph{model}
and a \emph{procedure}: The model aims to organize common security terminology in a reasonable and practical way, the procedure describes a method to analysis the IT system based on that model. In section \ref{subsec:priv-rec} we provide specific privacy recommendations as a result of the previous analysis that the operated system must comply.

@@

The \emph{world view} contains all components describing the current state.
It consists of the following components:
\begin{itemize}

@@

% \label{figure:Threats}
%input{./figures/Threats}
\begin{figure}
\centering
%\includegraphics[width=\textwidth]{diagrams/png/threat-table.png}
\newcommand{\tcell}[1]{\parbox[c]{6cm}{#1\vspace{3mm}}}
\newcommand{\thead}[1]{\tcell{\vspace{3mm}\centering\textbf{#1}}}
\newcommand{\tbody}[1]{\tcell{\footnotesize\flushleft #1}}
\resizebox{\textwidth}{!}{
\begin{tabular}{|c|c|c|c|}

\hline
\thead{Threat}
& \thead{Conflict of Interest}
& \thead{Vulnerability}
& \thead{Affected Data}
\\\hline\hline
\tbody{Insufficient Control Features}
& \tbody{Privacy vs. System Complexity}
& \tbody{Missing Privacy Awareness}
& \tbody{All collected data}
\\\hline

\tbody{Exessive Data Mining}
& \tbody{Privacy vs. Business Intelligence (LA),
\\Privacy vs. Financial Profit (SP)}
& \tbody{Lax data handling policies
\\Missing Privacy Awareness
\\Weak law enforcement}
& \tbody{Mined Information}
\\\hline

\tbody{Data Theft}
& \tbody{Privacy vs. Financial Profit
\\Reputation (SP) vs. Political Activism
\\Reputation (LA) vs. Political Activism}
& \tbody{Insecure Infrastructure,
\\Insecure Communication}
& \tbody{Transmitted data 
\\Data stored in data center}
\\\hline

\tbody{Surveillance}
& \tbody{Privacy vs. External Power}
& \tbody{Insecure Infrastructure
\\Insecure Communication}
& \tbody{Transmitted data 
\\Data stored in data center}
\\\hline

\tbody{Information Leak}
& \tbody{Privacy vs. Financial Profit
\\Reputation (SP) vs. Political Activism
\\Reputation (LA) vs. Political Activism}
& \tbody{Unhappy Employee 
\\Lax Access Rules}
& \tbody{Data stored in data center}
\\\hline

\tbody{Social Engineering}
& \tbody{Privacy vs. Financial Profit
\\Reputation (SP) vs. Political Activism
\\Reputation (LA) vs. Political Activism}
& \tbody{Unhappy Employee
\\Lax Access Rules}
& \tbody{Data stored in data center}
\\\hline
\end{tabular}
}
\caption{Threats}
\label{figure:Threats}
\end{figure}

@@

In this section we will associate to every identified threat a corresponding risk. A risk is the expected loss that is associated to the threat.
Therefore, we have to quantify the likeliness of the threat to occure and the harm or loss done in this case.
The quantification of likeliness will be solely based on rough judgment of the authors.
The quantification of loss, will be made in a two step process.
For each threat listed in table \ref{figure:Threats}, we have analyzed the affected personal data of the citizen.
For each possible data type (e.g. GPS) we analyze the impact on the seven different types of privacy in Section \ref{sec:SensorPrivacyImpact}.
In combination we can quantify roughly the impact of each threat on the citizens privacy. Both evaluations are necessarily fraught with a high level of uncertainty.

>>>>

In section \ref{subsec:world-analysis} and \ref{subsec:pot-analysis} we apply the first two steps of the Reference Model for IT Security Analysis as described in \cite{Grimm:ItSecRefModel}.  It supersedes earlier efforts by
e.g. \cite{Avizienis}.  The reference model consists of a \emph{model}
and a \emph{procedure}: The model aims to organize common security terminology in a reasonable and practical way. The procedure describes a method to analysis the IT system based on that model. In these sections we give a brief overview over the reference model by applying it to our scenario.

In section \ref{subsec:priv-rec} we provide specific privacy recommendations and requirements as a result of the previous analysis that the system must comply with.

@@

The first step is the \emph{world view} where all components are described in their current state. It consists of the following components:
\begin{itemize}

@@

@@

In this section we will associate to every identified threat a corresponding risk. A risk is the expected loss that is associated to the threat.
Therefore, we have to quantify the likeliness of the threat to occure and the harm or loss done in this case.
The quantification of likeliness will be solely based on rough judgment of the authors.
The quantification of loss, will be made in a two step process.
For each threat listed in the previous section, we have analyzed the affected personal data of the citizen.
For each possible data type (e.g. GPS) we analyze the impact on the seven different types of privacy in Section \ref{sec:SensorPrivacyImpact}.
In combination we can quantify roughly the impact of each threat on the citizens privacy. Both evaluations are necessarily fraught with a high level of uncertainty.
